\pkg{casebase}: An Alternative Framework For Survival Analysis and Comparison of Event Rates

### 2020-08-20 analysis/paper/paper.tex
included text for time-dependent Hazard Ratio

To illustrate these functions, we will use the European Randomized Study
of Prostate Cancer Screening (ERSPC) data \citep{schroder2009screening}
which was extracted using the approach described in Liu \emph{et al.}
\citeyearpar{liu2014recovering} This dataset is available through the
\pkg{casebase} package. It contains the individual observations for
159,893 men from seven European countries, who were between the ages of
55 and 69 years when recruited for the trial.

@@

\begin{CodeInput}
R> pt_object <- casebase::popTime(ERSPC, 
R+                                time = "Follow.Up.Time",
R+                                event = "DeadOfPrCa",
R+                                exposure = "ScrArm")
R> inherits(pt_object, "popTime")
\end{CodeInput}

@@

\caption[Population time plot for ERSPC data]{Population time plot for ERSPC data.}\label{fig:plot-stratified-erspc-data}
\end{figure}
\end{CodeChunk}

@@

For our first case study, we return to the ERSPC study and investigate
the differences in survival between the control and screening arms. We
fit four models that differ in which functional form of time is used: 1)
excluded from the linear predictor, 2) linear function, 3) log function,
and 4) a smooth function using cubic B-splines. The models are fit using
\code{fitSmoothHazard}. Since the output object from
\code{fitSmoothHazard} inherits from the \code{glm} class, we can
directly use the function \code{summary}:

@@

\begin{CodeInput}
R> fmla <- list(exponential = as.formula(DeadOfPrCa ~ ScrArm),
R>              gompertz = as.formula(DeadOfPrCa ~ Follow.Up.Time + ScrArm),
R>              weibull = as.formula(DeadOfPrCa ~ log(Follow.Up.Time) + ScrArm),
R>              splines = as.formula(DeadOfPrCa ~ bs(Follow.Up.Time) + ScrArm))
R> 
R> fits <- lapply(fmla, function(i) {
R>   casebase::fitSmoothHazard(i, data = ERSPC, ratio = 100)
R> })
R> 
R> summary(fits[["gompertz"]])
\end{CodeInput}
\end{CodeChunk}

@@

\begin{CodeOutput}
#> 
#> Call:
#> glm(formula = formula, family = binomial, data = sampleData)
#> 
#> Deviance Residuals: 
#>    Min      1Q  Median      3Q     Max  
#> -0.378  -0.162  -0.122  -0.094   3.468  
#> 
#> Coefficients:
#>                       Estimate Std. Error z value            Pr(>|z|)    
#> (Intercept)            -9.0335     0.1122  -80.54 <0.0000000000000002 ***
#> Follow.Up.Time          0.2228     0.0145   15.32 <0.0000000000000002 ***
#> ScrArmScreening group  -0.2340     0.0886   -2.64              0.0083 ** 
#> ---
#> Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
#> 
#> (Dispersion parameter for binomial family taken to be 1)
#> 
#>     Null deviance: 6059.0  on 54539  degrees of freedom
#> Residual deviance: 5810.1  on 54537  degrees of freedom
#> AIC: 5816
#> 
#> Number of Fisher Scoring iterations: 8
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeInput}
R> new_data <- data.frame(ScrArm = c("Control group", "Screening group"))
R> 
R> risks <- lapply(fits, function(i) {
R>   casebase::absoluteRisk(object = i, time = seq(0,15,0.1), newdata = new_data)
R> })
R> 
R> head(risks[["gompertz"]])
\end{CodeInput}
\end{CodeChunk}

In Figure \ref{fig:erspc-cox-cif}, we overlay the estimated CIFs from
\pkg{casebase} on the Cox model CIF. The CIF estimates for the
exponential model in panel (1) overestimate the cumulative incidence
earlier on in time, and underestimate it later on. Based on our earlier
discussion of the population-time plot, this poor fit for the
exponential hazard was expected.

In Figure \ref{fig:erspc-cox-cif} (panels 2--4), we notice a better fit
with increasing complexity of our model for time. As noted above, the
usual asymptotic results hold for likelihood ratio tests built using
case-base sampling models. Therefore, we can easily test the null
hypothesis that the exponential model is just as good as the larger (in
terms of number of parameters) splines model:

@@

\begin{CodeOutput}
#> Analysis of Deviance Table
#> 
#> Model 1: DeadOfPrCa ~ ScrArm + offset(offset)
#> Model 2: DeadOfPrCa ~ bs(Follow.Up.Time) + ScrArm + offset(offset)
#>   Resid. Df Resid. Dev Df Deviance            Pr(>Chi)    
#> 1     54538       6053                                    
#> 2     54535       5787  3      266 <0.0000000000000002 ***
#> ---
#> Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
\end{CodeOutput}
\end{CodeChunk}

As expected, we see that splines model provides a better fit. Similarly,
we can compare the AIC for all four case-base models:

@@

\begin{CodeOutput}
#>    Exp.   Gomp.   Weib. Splines 
#>    6057    5816    6057    5797
\end{CodeOutput}
\end{CodeChunk}

Once again, we have evidence that the splines model provides the best
fit.

{\centering \includegraphics[width=\textwidth,keepaspectratio=true]{../figures/erspc-cox-cif-1}

\caption{CIFs for control and screening groups in the ERSPC data. In each of the panels, we plot the CIF from the Cox model using \code{survival::survfit} (solid line) and the CIF from the case-base sampling scheme (dashed line) with different functional forms of time. (1) The time variable is excluded (exponential). (2) Linear function of time (Gompertz). (3) The natural logarithm (Weibull). (4) Cubic B-spline expansion of time.}\label{fig:erspc-cox-cif}
\end{figure}
\end{CodeChunk}

In the following table, we present a side-by-side comparison of the
hazard ratios and confidence intervals estimated from
\code{fitSmoothHazard} and the corresponding parametric model using
\code{survival::survreg}, as well as the Cox model estimate. The hazard
ratio estimates and confidence intervals are similar across all four
models. This reinforces the idea that, under proportional hazards, we do
not need to model the full hazard to obtain reliable estimates of the
hazard ratio. Nevertheless, Figure \ref{fig:erspc-cox-cif} shows that
different parametric models can still give rise to qualitatively
different estimates for the CIF.

@@

With this first case study, we explored how \pkg{casebase} allows us to
fit different parametric survival models, and how we can compare the fit
of each model with tools from GLMs.

@@

\caption{\label{tab:bmtcrr-cis}Estimates and confidence intervals for the hazard ratios for each coefficient. Both estimates from case-base sampling and Cox regression are presented.}
\centering
\begin{tabular}[t]{lrlrl}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Case-Base} & \multicolumn{2}{c}{Cox} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
Covariates & HR & 95\% CI & HR & 95\% CI\\
\midrule
Sex & 0.70 & (0.4, 1.23) & 0.68 & (0.39, 1.19)\\
Disease & 0.53 & (0.29, 0.95) & 0.52 & (0.29, 0.93)\\
Phase (CR2 vs. CR1) & 1.12 & (0.45, 2.78) & 1.21 & (0.48, 3.02)\\
Phase (CR3 vs. CR1) & 1.45 & (0.37, 5.66) & 1.67 & (0.43, 6.5)\\
Phase (Relapse vs. CR1) & 4.04 & (1.88, 8.68) & 4.55 & (2.09, 9.9)\\
\addlinespace
Source & 1.48 & (0.48, 4.54) & 1.46 & (0.47, 4.54)\\
Age & 0.99 & (0.97, 1.01) & 0.99 & (0.97, 1.02)\\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{CodeOutput}
#> Model1 Model2 Model3 
#>    827    790    788
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeOutput}
#> [1] "absRiskCB" "matrix"    "array"
\end{CodeOutput}

@@

\begin{center}\includegraphics[width=\textwidth,keepaspectratio=true]{../figures/unnamed-chunk-9-1} \end{center}

@@

This report was generated on 2020-08-06 17:31:23 using the following
computational environment and dependencies:

@@

\begin{CodeOutput}
#> R version 4.0.2 (2020-06-22)
#> Platform: x86_64-apple-darwin17.0 (64-bit)
#> Running under: macOS Catalina 10.15.6
#> 
#> Matrix products: default
#> BLAS:   /Library/Frameworks/R.framework/Versions/4.0/Resources/lib/libRblas.dylib
#> LAPACK: /Library/Frameworks/R.framework/Versions/4.0/Resources/lib/libRlapack.dylib
#> 
#> locale:
#> [1] en_CA.UTF-8/en_CA.UTF-8/en_CA.UTF-8/C/en_CA.UTF-8/en_CA.UTF-8
#> 
#> attached base packages:
#> [1] splines   stats     graphics  grDevices utils     datasets  methods  
#> [8] base     
#> 
#> other attached packages:
#>  [1] broom_0.5.6               dotwhisker_0.5.0         
#>  [3] timereg_1.9.4             glue_1.4.1               
#>  [5] scales_1.1.1              forcats_0.5.0            
#>  [7] stringr_1.4.0             dplyr_1.0.0              
#>  [9] purrr_0.3.4               readr_1.3.1              
#> [11] tidyr_1.0.2               ggplot2_3.3.2            
#> [13] tidyverse_1.3.0           lubridate_1.7.8          
#> [15] visreg_2.6.1              tibble_3.0.3             
#> [17] riskRegression_2020.02.05 prodlim_2019.11.13       
#> [19] flexsurv_1.1.1            survival_3.1-12          
#> [21] pracma_2.2.9              magrittr_1.5             
#> [23] kableExtra_1.1.0          glmnet_3.0-2             
#> [25] Matrix_1.2-18             data.table_1.12.8        
#> [27] cowplot_1.0.0             colorspace_1.4-1         
#> [29] casebase_0.9.0.9000      
#> 
#> loaded via a namespace (and not attached):
#>  [1] TH.data_1.0-10      VGAM_1.1-2          ellipsis_0.3.1     
#>  [4] ggstance_0.3.4      htmlTable_1.13.3    base64enc_0.1-3    
#>  [7] fs_1.4.1            rstudioapi_0.11     farver_2.0.3       
#> [10] MatrixModels_0.4-1  fansi_0.4.1         mvtnorm_1.1-0      
#> [13] xml2_1.3.2          codetools_0.2-16    knitr_1.29         
#> [16] Formula_1.2-3       jsonlite_1.6.1      cluster_2.1.0      
#> [19] dbplyr_1.4.3        png_0.1-7           compiler_4.0.2     
#> [22] httr_1.4.1          backports_1.1.8     assertthat_0.2.1   
#> [25] cli_2.0.2           acepack_1.4.1       htmltools_0.5.0    
#> [28] quantreg_5.55       tools_4.0.2         gtable_0.3.0       
#> [31] Rcpp_1.0.5          cellranger_1.1.0    vctrs_0.3.2        
#> [34] nlme_3.1-148        iterators_1.0.12    xfun_0.15          
#> [37] rvest_0.3.5         lifecycle_0.2.0     polspline_1.1.17   
#> [40] muhaz_1.2.6.1       MASS_7.3-51.6       zoo_1.8-8          
#> [43] hms_0.5.3           sandwich_2.5-1      SparseM_1.78       
#> [46] RColorBrewer_1.1-2  rticles_0.14        yaml_2.2.1         
#> [49] gridExtra_2.3       rms_5.1-4           rpart_4.1-15       
#> [52] latticeExtra_0.6-29 stringi_1.4.6       foreach_1.5.0      
#> [55] checkmate_2.0.0     lava_1.6.7          shape_1.4.4        
#> [58] rlang_0.4.7         pkgconfig_2.0.3     evaluate_0.14      
#> [61] lattice_0.20-41     labeling_0.3        htmlwidgets_1.5.1  
#> [64] cmprsk_2.2-9        tidyselect_1.1.0    deSolve_1.28       
#> [67] R6_2.4.1            generics_0.0.2      Hmisc_4.4-0        
#> [70] multcomp_1.4-13     DBI_1.1.0           withr_2.2.0        
#> [73] pillar_1.4.6        haven_2.2.0         foreign_0.8-80     
#> [76] mgcv_1.8-31         nnet_7.3-14         mstate_0.2.12      
#> [79] modelr_0.1.6        crayon_1.3.4        rmarkdown_2.1      
#> [82] jpeg_0.1-8.1        grid_4.0.2          readxl_1.3.1       
#> [85] reprex_0.3.0        digest_0.6.25       webshot_0.5.2      
#> [88] numDeriv_2016.8-1.1 stats4_4.0.2        munsell_0.5.0      
#> [91] viridisLite_0.3.0   quadprog_1.5-8
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeOutput}
#> Local:    Jesse-Islam-master /Users/maxturgeon/Documents/git_repos/cbpaper
#> Head:     [32e6bf4] 2020-08-05: Merge pull request #25 from sahirbhatnagar/editMax
\end{CodeOutput}
\end{CodeChunk}

>>>>

To illustrate these functions, we will use data from the European
Randomized Study of Prostate Cancer Screening (ERSPC)
\citep{schroder2009screening} which was extracted using the approach
described in Liu \emph{et al.} \citeyearpar{liu2014recovering} This
dataset is available through the \pkg{casebase} package. It contains the
individual observations for 159,893 men from seven European countries,
who were between the ages of 55 and 69 years when recruited for the
trial.

@@

\begin{CodeInput}
R> pt_object <- casebase::popTime(ERSPC, time = "Follow.Up.Time",
R+                                event = "DeadOfPrCa", exposure = "ScrArm")
R> inherits(pt_object, "popTime")
\end{CodeInput}

@@

\caption[Population time plots for both treatment arms in the ERSPC dataset]{Population time plots for both treatment arms in the ERSPC dataset. The grey area can be thought of as N=88,232 (control group) and N=71,661 (screening group) rows of infinitely small rectangles (person-moments). The points shown in the figure are select person-moments from the case and base series. We see that more events are observed at later follow-up times, motivating the use of a non-constant in time hazard model.}\label{fig:plot-stratified-erspc-data}
\end{figure}
\end{CodeChunk}

@@

For our first case study, we return to the ERSPC study and investigate
the differences in risk between the control and screening arms. We fit
four models that differ in which functional form of time is used: 1)
excluded from the linear predictor, 2) linear function, 3) log function,
and 4) a smooth function using cubic B-splines. The models are fit using
\code{fitSmoothHazard} with the familiar formula interface:

@@

\begin{CodeInput}
R> fmla <- list(exponential = as.formula(DeadOfPrCa ~ ScrArm),
R+              gompertz = as.formula(DeadOfPrCa ~ Follow.Up.Time + ScrArm),
R+              weibull = as.formula(DeadOfPrCa ~ log(Follow.Up.Time) + ScrArm),
R+              splines = as.formula(DeadOfPrCa ~ bs(Follow.Up.Time) + ScrArm))
R> 
R> fits <- lapply(fmla, function(i) {
R+   fitSmoothHazard(i, data = ERSPC, ratio = 100)
R+ })
\end{CodeInput}
\end{CodeChunk}

The output object from \code{fitSmoothHazard} inherits from the
\code{singleEventCB} and \code{glm} classes. As such, we can directly
use the \code{summary} generic:

@@

\begin{CodeInput}
R> summary(fits[["splines"]]) 
\end{CodeInput}
\end{CodeChunk}

\begin{CodeOutput}
#> 
#> Coefficients:
#>                       Estimate Std. Error z value Pr(>|z|)
#> (Intercept)           -10.2905     0.3185  -32.31  < 2e-16
#> bs(Follow.Up.Time)1     4.3587     0.8008    5.44  5.2e-08
#> bs(Follow.Up.Time)2     2.0890     0.4721    4.42  9.7e-06
#> bs(Follow.Up.Time)3     4.6266     0.6910    6.70  2.1e-11
#> ScrArmScreening group  -0.2354     0.0886   -2.66   0.0079
#> 
#> (Dispersion parameter for binomial family taken to be 1)
#> 
#>     Null deviance: 6059.0  on 54539  degrees of freedom
#> Residual deviance: 5785.3  on 54535  degrees of freedom
#> AIC: 5795
#> 
#> Number of Fisher Scoring iterations: 9
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeInput}
R> new_data <- data.frame(ScrArm = c("Control group", "Screening group"))
R> new_time <- seq(0,14,0.1)
R> 
R> risks <- lapply(fits, function(i) {
R>   absoluteRisk(object = i, time = new_time, newdata = new_data, method = "mont")
R> })
\end{CodeInput}
\end{CodeChunk}

In Figure \ref{fig:erspc-cox-cif}, we overlay the estimated CIFs from
\pkg{casebase} on the Cox model CIF. The CIF estimates for the
exponential model in panel (1) overestimate the cumulative incidence
earlier on in time, and underestimate it later on. Based on our earlier
discussion of the population-time plot, this poor fit for the
exponential hazard was expected. We notice a better fit with increasing
complexity of our model for time in Figure \ref{fig:erspc-cox-cif}
(panels 2--4). As noted above, the usual asymptotic results hold for
likelihood ratio tests built using case-base sampling models. Therefore,
we can easily test the null hypothesis that the Weibull model is just as
good as the larger (in terms of number of parameters) spline model:

@@

\begin{CodeOutput}
#> Analysis of Deviance Table
#> 
#> Model 1: DeadOfPrCa ~ log(Follow.Up.Time) + ScrArm + offset(offset)
#> Model 2: DeadOfPrCa ~ bs(Follow.Up.Time) + ScrArm + offset(offset)
#>   Resid. Df Resid. Dev Df Deviance Pr(>Chi)    
#> 1     54537       5801                         
#> 2     54535       5785  2     15.7    4e-04 ***
#> ---
#> Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
\end{CodeOutput}
\end{CodeChunk}

The null hypothesis is rejected in favor of the spline model. Similarly,
the AIC provides further evidence that the flexible function of time
provides the best fit:

@@

\begin{CodeOutput}
#>     Exp. Gompertz  Weibull  Splines 
#>     6056     5821     5807     5795
\end{CodeOutput}
\end{CodeChunk}

\begin{CodeChunk}
\begin{figure}
\includegraphics[width=\textwidth,keepaspectratio=true]{../figures/erspc-cox-cif-1} \caption{CIFs for control and screening groups in the ERSPC data. In each of the panels, we plot the CIF from the Cox model using \code{survival::survfit} (solid line) and the CIF from the case-base sampling scheme (dashed line) with different functional forms of time. (1) The time variable is excluded (exponential). (2) Linear function of time (Gompertz). (3) The natural logarithm (Weibull). (4) Cubic B-spline expansion of time.}\label{fig:erspc-cox-cif}
\end{figure}
\end{CodeChunk}

In Table \ref{tab:print-erspc-estimates}, we present a side-by-side
comparison of the hazard ratios and confidence intervals estimated from
\code{fitSmoothHazard} and the corresponding parametric model using
\code{survival::survreg}, as well as the Cox model estimate. The hazard
ratio estimates and confidence intervals are similar across all four
models. This reinforces the idea that, under proportional hazards, we do
not need to model the full hazard to obtain reliable estimates of the
hazard ratio. Nevertheless, Figure \ref{fig:erspc-cox-cif} shows that
different parametric models can still give rise to qualitatively
different estimates for the CIF.

@@

Previous re-analyses of these data suggested that the overall screening
attributed reduction in death due to prostate cancer of 20\% was an
underestimate \citep{hanley2010mortality}. The estimated 20\% (from a
proportional hazards model) did not account for the delay between
screening and the time the effect is expected to be observed. As a
result, the null effects in years 1--7 masked the substantial reductions
that began to appear from year 8 onwards. This motivates the use of a
time-dependent hazard ratio which can easily be fit with the
\pkg{casebase} package by including an interaction term with time in the
model:

\begin{CodeInput}
R> fit_inter <- fitSmoothHazard(DeadOfPrCa ~ bs(Follow.Up.Time) * ScrArm, data = ERSPC)
\end{CodeInput}
\end{CodeChunk}

In Figure \ref{fig:interaction-ERSPC} we plot the estimated death from
prostate cancer hazard ratio and 95\textbackslash\% confidence interval
for screening vs.~control group as a function of time using the
\code{plot} method for objects of class \code{singleEventCB}:

\begin{CodeInput}
R> plot(fit_inter, type = "hr", newdata = new_data,
R>      var = "ScrArm", xvar = "Follow.Up.Time", ci = TRUE)
\end{CodeInput}
\end{CodeChunk}

The plot shows that the cures attributable to the screening only begin
to become statistically apparent by year 7 and later. The 25-60\%
reductions seen in years 8-12 of the study suggests a much higher
reduction in prostate cancer due to screening than the single overall
20\% reported in the original article.

{\centering \includegraphics[width=\textwidth,keepaspectratio=true]{../figures/interaction-ERSPC-1}

\caption[Estimated death from prostate cancer hazard ratio and 95\% confidence interval for screening vs]{Estimated death from prostate cancer hazard ratio and 95\% confidence interval for screening vs. control group as a function of time in the ERSPC dataset. Hazard ratios are estimated from fitting a parametric hazard model as a function of the interaction between a cubic B-spline basis of follow-up time and treatment arm. 95\% confidence intervals are calculated using the delta method. The plot shows that the cures attributable to the screening only begin to become statistically apparent by year 7 and later. The 25-60\% reductions seen in years 8-12 of the study suggests a much higher reduction in prostate cancer due to screening than the single overall 20\% reported in the original article.}\label{fig:interaction-ERSPC}
\end{figure}
\end{CodeChunk}

With this first case study, we explored how \pkg{casebase} allows us to
fit different parametric survival models with possible time-varying
effects, and how we can compare the fit of each model with tools from
GLMs.

\newpage

@@

\caption{\label{tab:bmtcrr-cis}Estimates and confidence intervals for the hazard ratios for each coefficient. Both estimates from case-base sampling and Cox regression are presented.}
\centering
\begin{tabular}[t]{lrlrl}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Case-Base} & \multicolumn{2}{c}{Cox} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
Covariates & HR & 95\% CI & HR & 95\% CI\\
\midrule
Sex & 0.72 & (0.42, 1.26) & 0.68 & (0.39, 1.19)\\
Disease & 0.54 & (0.3, 0.97) & 0.52 & (0.29, 0.93)\\
Phase (CR2 vs. CR1) & 1.21 & (0.48, 3.02) & 1.21 & (0.48, 3.02)\\
Phase (CR3 vs. CR1) & 1.63 & (0.41, 6.44) & 1.67 & (0.43, 6.5)\\
Phase (Relapse vs. CR1) & 4.43 & (2.06, 9.55) & 4.55 & (2.09, 9.9)\\
\addlinespace
Source & 1.51 & (0.49, 4.69) & 1.46 & (0.47, 4.54)\\
Age & 0.99 & (0.97, 1.01) & 0.99 & (0.97, 1.02)\\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{CodeOutput}
#> Model1 Model2 Model3 
#>    827    793    792
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeOutput}
#> [1] "absRiskCB" "matrix"
\end{CodeOutput}

@@

\begin{center}\includegraphics[width=\textwidth,keepaspectratio=true]{../figures/unnamed-chunk-11-1} \end{center}

@@

This report was generated on 2020-08-20 19:21:21 using the following
computational environment and dependencies:

@@

\begin{CodeOutput}
#> R version 3.6.2 (2019-12-12)
#> Platform: x86_64-pc-linux-gnu (64-bit)
#> Running under: Pop!_OS 19.10
#> 
#> Matrix products: default
#> BLAS:   /usr/lib/x86_64-linux-gnu/openblas/libblas.so.3
#> LAPACK: /usr/lib/x86_64-linux-gnu/libopenblasp-r0.3.7.so
#> 
#> locale:
#>  [1] LC_CTYPE=en_US.UTF-8       LC_NUMERIC=C              
#>  [3] LC_TIME=en_US.UTF-8        LC_COLLATE=en_US.UTF-8    
#>  [5] LC_MONETARY=en_US.UTF-8    LC_MESSAGES=en_US.UTF-8   
#>  [7] LC_PAPER=en_US.UTF-8       LC_NAME=C                 
#>  [9] LC_ADDRESS=C               LC_TELEPHONE=C            
#> [11] LC_MEASUREMENT=en_US.UTF-8 LC_IDENTIFICATION=C       
#> 
#> attached base packages:
#> [1] splines   stats     graphics  grDevices utils     datasets  methods  
#> [8] base     
#> 
#> other attached packages:
#>  [1] scales_1.1.1              forcats_0.5.0            
#>  [3] stringr_1.4.0             dplyr_1.0.0              
#>  [5] purrr_0.3.4               readr_1.3.1              
#>  [7] tidyr_1.1.0               ggplot2_3.3.2.9000       
#>  [9] tidyverse_1.3.0           lubridate_1.7.4          
#> [11] visreg_2.7.0              tibble_3.0.1             
#> [13] riskRegression_2020.02.05 prodlim_2019.11.13       
#> [15] flexsurv_1.1.1            survival_3.1-8           
#> [17] pracma_2.2.9              magrittr_1.5             
#> [19] kableExtra_1.1.0          glmnet_4.0-2             
#> [21] Matrix_1.2-18             data.table_1.12.8        
#> [23] cowplot_1.0.0             colorspace_1.4-1         
#> [25] casebase_0.9.0           
#> 
#> loaded via a namespace (and not attached):
#>  [1] TH.data_1.0-10      VGAM_1.1-3          ellipsis_0.3.1     
#>  [4] htmlTable_1.13.3    base64enc_0.1-3     fs_1.3.2           
#>  [7] rstudioapi_0.11     MatrixModels_0.4-1  fansi_0.4.1        
#> [10] mvtnorm_1.0-12      xml2_1.3.0          codetools_0.2-16   
#> [13] knitr_1.29          Formula_1.2-3       jsonlite_1.7.0     
#> [16] broom_0.7.0         cluster_2.1.0       dbplyr_1.4.2       
#> [19] png_0.1-7           compiler_3.6.2      httr_1.4.1         
#> [22] backports_1.1.8     assertthat_0.2.1    cli_2.0.2          
#> [25] acepack_1.4.1       htmltools_0.5.0     quantreg_5.54      
#> [28] tools_3.6.2         gtable_0.3.0        glue_1.4.1         
#> [31] Rcpp_1.0.4.6        cellranger_1.1.0    vctrs_0.3.1        
#> [34] nlme_3.1-143        iterators_1.0.12    xfun_0.15          
#> [37] rvest_0.3.5         lifecycle_0.2.0     polspline_1.1.17   
#> [40] muhaz_1.2.6.1       MASS_7.3-51.5       zoo_1.8-7          
#> [43] hms_0.5.3           sandwich_2.5-1      SparseM_1.78       
#> [46] RColorBrewer_1.1-2  rticles_0.13        yaml_2.2.1         
#> [49] gridExtra_2.3       rms_5.1-4           rpart_4.1-15       
#> [52] latticeExtra_0.6-29 stringi_1.4.6       foreach_1.5.0      
#> [55] checkmate_2.0.0     lava_1.6.6          shape_1.4.4        
#> [58] rlang_0.4.6         pkgconfig_2.0.3     evaluate_0.14      
#> [61] lattice_0.20-38     htmlwidgets_1.5.1   cmprsk_2.2-9       
#> [64] tidyselect_1.1.0    deSolve_1.27.1      R6_2.4.1           
#> [67] generics_0.0.2      Hmisc_4.3-1         multcomp_1.4-12    
#> [70] DBI_1.1.0           withr_2.2.0         pillar_1.4.4       
#> [73] haven_2.3.1         foreign_0.8-74      mgcv_1.8-31        
#> [76] nnet_7.3-12         mstate_0.2.12       modelr_0.1.5       
#> [79] crayon_1.3.4        rmarkdown_2.3       timereg_1.9.4      
#> [82] jpeg_0.1-8.1        grid_3.6.2          readxl_1.3.1       
#> [85] reprex_0.3.0        digest_0.6.25       webshot_0.5.2      
#> [88] numDeriv_2016.8-1.1 stats4_3.6.2        munsell_0.5.0      
#> [91] viridisLite_0.3.0   quadprog_1.5-8
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeOutput}
#> Local:    fix-cs1 /home/sahir/git_repositories/cbpaper
#> Remote:   fix-cs1 @ origin (https://github.com/sahirbhatnagar/cbpaper.git)
#> Head:     [f618e21] 2020-08-18: time dependent hazard ratio for ERSPC
\end{CodeOutput}
\end{CodeChunk}
